robspack An R package for processing atmospheric greenhouse gas observations in NOAA's ObsPack

### 2023-10-03 paper_elsevier/paper_elsevier.Rmd
adding NetCDF support

categories <- c("aircraft-pfp","aircraft-insitu","surface-insitu",
  "aircore","surface-pfp","tower-insitu","shipboard-insitu","flask")
obs <- "../../../obspack_ch4_1_GLOBALVIEWplus_v4.0_2021-10-14/data/txt"
index <- obs_summary(obs = obs, verbose = F)
```

```{r kable, echo = FALSE}
ta <- obs_summary(obs = obs, verbose = F, aslist = TRUE)$summary
knitr::kable(ta, format = "latex", caption = "Summary of ObsPack")
```

@@

```{r sf, echo = FALSE, message=FALSE}
library(sf)
library(ggplot2)
dft <- obs_table(index =  index, categories = "tower-insitu")
dft <- dft[stat == "mean"]
sdft <- st_as_sf(dft, coords = c("longitude", "latitude"), crs = 4326)
sdft$value <- sdft$value*1e09

>>>>

categories <- c("aircraft-pfp","aircraft-insitu","surface-insitu",
  "aircore","surface-pfp","tower-insitu","shipboard-insitu","flask")
obs <- "../../../obspack_ch4_1_GLOBALVIEWplus_v4.0_2021-10-14/data/txt"
index <- obs_summary(obs = obs, 
                     categories = c("aircraft",
                                    "surface",
                                    "aircore",
                                    "shipboard",
                                    "tower"),
                     verbose = T)
```

```{r kable, echo = FALSE}
ta <- obs_summary(obs = obs, 
                  categories =  c("aircraft",
                                    "surface",
                                    "aircore",
                                    "shipboard",
                                    "tower"),
                  verbose = F, aslist = TRUE)$summary
knitr::kable(ta, format = "latex", caption = "Summary of ObsPack")
```

@@

```{r sf, echo = FALSE, message=FALSE}
library(sf)
library(ggplot2)
dft <- obs_table(index =  index, categories = "tower")
dft <- dft[stat == "mean"]
sdft <- st_as_sf(dft, coords = c("longitude", "latitude"), crs = 4326)
sdft$value <- sdft$value*1e09
